### 2018-07-23 response-to-reviewers.tex

% -*- mode: LaTeX; mode: flyspell; -*-
% mode: Tex-Pdf -*-
\documentclass{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[bookmarks=TRUE,
            colorlinks,
            pdfpagemode=none,
            pdfstartview=FitH,
            citecolor=black,
            filecolor=black,
            linkcolor=blue,
            urlcolor=black,
            ]{hyperref}
\usepackage[top=15mm, bottom=25mm, left=10mm, textwidth=130mm,
marginparwidth=70mm]{geometry}
\usepackage{graphicx}
\usepackage{icomma}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{xspace}
\usepackage{csquotes}
\usepackage[layout=margin,author=,status=draft]{fixme}

\fxsetup{theme=color}
\newcommand{\skb}[1]{
	\begin{quotation}
		\color{Blue} SKB: #1	
	\end{quotation}
}
\newcommand{\debug}[1]{\marginpar{\small\raggedright\begin{spacing}{1}
      \color{BrickRed} #1
\end{spacing}
}}
\newenvironment{response}
{\slshape}{}
\date{}
\title{Response to the referees and editor}
\begin{document}

\section{Comments by the editor}

%\enquote{You will be unable to make your revisions on the originally submitted version of the manuscript.  Instead, revise your manuscript using a word processing program and save it on your computer.  Please also highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or coloured text. }
%We used LaTeX to prepare the manuscript and were not able to use MS Word to track the changes. Instead we uploaded a PDF-file that shows the differences between our original submission and the revised text. We hope that this file satisfies the requirements.

@@

\section{Referee: 2}

\subsection{Additional Questions:}

\subsubsection*{4. Results}

\begin{enumerate}
%\item For this papers findings section in the abstract they imply that
%  for all men fluency in Estonian is related to 5\% lower unemployment
%  and no income premium.  From Table 2 and 3 it appears that this
%  should be for only Russian males. English skills are associated with
%  a large income premium and no unemployment. From Table 2 and 3 this
%  appears to be more accurately just Russians, as the Estonians appear
%  to have a significant negative correlation with unemployment.  This
%  is supported by what is said later in the Discussion and Concluding
%  Remarks section in what they state is their most intriguing
%  observation.  Claiming this to be the most intriguing is interesting
%  as it seems to support some what previous literature has stated and
%  one of the extensions that this paper is making the inclusion of
%  women and namely how their effects differ from males and previous
%  literature. 
%
%  \begin{response}
%    No response needed here.
%  \end{response}
